Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-06-29 experiement.tex
add model explanation

As it can be observed in Figures \ref{fig:case1}, \ref{fig:case2} and
\ref{fig:case3}, the different cascade levels required up to $2n+1$ timesteps
before it starts to enrich uranium, where $n$ corresponds to the level number.
This corresponds to the number of timesteps required for the material to
propagate from the natural uranium source to the $n$-th level, regardless of the
duration of the timestep (hour, day, month, etc.). This is also true for the
number of timesteps required to reach the equilibrium assays value in the tails
reprocessing cases.  As timestep can be artificially small or large, one will
only be considering equilibrium values of flow rates and assays in the following
analysis.

>>>>

The different cascade levels required up to $2n+1$ timesteps
before it starts to enrich uranium, where $n$ corresponds to the level number.
This corresponds to the number of timesteps required for the material to
propagate from the natural uranium source to the $n$-th level, regardless of the
duration of the timestep (hour, day, month, etc.). This is also true for the
number of timesteps required to reach the equilibrium assays value in the tails
reprocessing cases.  As timestep can be artificially small or large, one will
only be considering equilibrium values of flow rates and assays in the following
analysis.

### 2018-06-29 results.tex
add model explanation

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.2]{feed_assays}
        \caption{Feed Assays.}
        \label{sfig:feed_assay}
    \end{subfigure}%
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.2]{product_assays}
        \caption{Product Assays.}
        \label{sfig:product_assay}
    \end{subfigure}
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.2]{tails_assays}
        \caption{Tails Assays.}
        \label{sfig:tails_assay}
    \end{subfigure}
    \caption{Feed (\subref{sfig:feed_assay}), product
        (\subref{sfig:product_assay}) and tails assays (\subref{sfig:tails_assay})
        in $m\%$ of $^{235}$U, per cascade level from 0 to 3 (red, green, orange,
        blue), per model (A/B/C) and without/with tails recycling (NR/R).}
    \label{fig:assays}
\end{figure}

>>>>

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.2]{feed_assays}
        \caption{Feed Assays.}
        \label{sfig:feed_assay}
    \end{subfigure}%
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.2]{product_assays}
        \caption{Product Assays.}
        \label{sfig:product_assay}
    \end{subfigure}
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.2]{tails_assays}
        \caption{Tails Assays.}
        \label{sfig:tails_assay}
    \end{subfigure}
    \caption{Feed (\subref{sfig:feed_assay}), product
        (\subref{sfig:product_assay}) and tails assays (\subref{sfig:tails_assay})
        in $m\%$ of $^{235}$U, per cascade level from 0 to 3 (red, green, orange,
        blue), per model (A/B/C) and without/with tails recycling (NR/R). The
        black dashed line represents the $90 m\%$ enrichment threshold.}
    \label{fig:assays}
\end{figure}

### 2018-06-29 theory.tex
add model explanation

@@

@@

>>>>

This model assumes that it is possible to maintain the separative power of a
centrifuges, $\delta U$, for any feed assays $N$ while maintaining its cut
$\theta$ and feed flow $F$.

@@

This model assumes that it is possible to tune a centrifuge separative power
$\delta U$, for any feed assay $N$, cut $\theta$ and feed flow $F$, in order to
maintain its constant feed to product enrichment factor $\alpha$.

@@

This model assumes that it is possible to tune the centrifuge separative power
$\delta U$ in order to maintain, for any feed assay $N$, its tails to product
enrichment factor $\gamma$, while maintaining its cut $\theta$ and feed flow
$F$.
